Meta-analysis

### 2020-07-31 04_MetaAnalysis.Rmd
Spelling
Add model contrasts to save data

The first table in this output shows the tau^2 (variance) of each random effects and the number of occurrences for each treatment in the analysis.
This effectively shows the heterogeneity between experiments for these partivular treatments.

@@

```{r Save_meta_data, eval=FALSE}
write.csv(slimmer_PM_dat, file = "data/GYmeta_data.csv")
save(dat1, efficacy, PM_mv, YieldContrasts, file = here("cache/Meta-analysisData.Rdata"))
```

>>>>

The first table in this output shows the tau^2 (variance) of each random effects and the number of occurrences for each treatment in the analysis.
This effectively shows the heterogeneity between experiments for these particular treatments.

@@

```{r Save_meta_data, eval=FALSE}
save(dat1, efficacy, slimmer_PM_dat, PM_mv, YieldContrasts,contrast_Ssum,file =
        here("cache/Meta-analysisData.Rdata"))
```
